Title of the Master Thesis

### 2015-07-15 Master Thesis/thesis.tex
Update bibliography
Update notation

\begin{theorem}[\textit{Neukirch-Uchida}]\label{thm:neukirch-uchida}
Let $k,k'$ be two global fields. Then any isomorphism $G_k\to G_{k'}$ is induced by a unique isomorphism $k'^s\to k^s$.  In particular, if $k,k'$ have isomorphic absolute Galois groups, they are isomorphic as fields.
\end{theorem}

@@

$\begin{array}{ll}
\mathbb{N} & \text{Natural numbers} \\
\mathbb{Z} & \text{Integers}\\
\mathbb{Q} & \text{Rational numbers}\\
\mathbb{R} & \text{Real numbers}\\
\mathbb{C} & \text{Complex numbers}\\
\mathbb{Z}_p & \text{$p$-adic integers}\\
\mathbb{Q}_p & \text{$p$-adic numbers}
\end{array}$

\chapter{First chapter}

\begin{thebibliography}{99999999}

\bibitem[DDMS99]{DDMS99}
	J. D. Dixon, M. P. F. du Sautoy, A. Mann, D. Segal (1999)
	\textit{Analytic Pro-$p$ Groups}.
	Cambridge Studies in Advanced Mathematics,
	2nd Edition.

>>>>

\begin{theorem}[\textit{Neukirch-Uchida}]\label{thm:neukirch-uchida}
Let $k,k'$ be two global fields. Then any isomorphism $G_k\to G_{k'}$ is induced by a unique isomorphism $k'^{\text{s}}\to k^\text{s}$.  In particular, if $k,k'$ have isomorphic absolute Galois groups, they are isomorphic as fields.
\end{theorem}

@@

$\begin{array}{ll}
\mathbb{N} & \text{natural numbers} \\
\mathbb{Z} & \text{integers}\\
\mathbb{Q} & \text{rational numbers}\\
\mathbb{R} & \text{real numbers}\\
\mathbb{C} & \text{complex numbers}\\
\mathbb{Z}_p & \text{$p$-adic integers}\\
\mathbb{Q}_p & \text{$p$-adic numbers}\\
\\
\overline{K} & \text{algebraic closure of $K$}\\
K^\text{s} & \text{separable closure of $K$}\\
G_K & \text{absolute Galois group of $K$}
\end{array}$

\mainmatter
\setcounter{page}{9}
\chapter{First chapter}

\begin{thebibliography}{99999}

\bibitem[Sp96]{Sp96}
	M. Spiess (1996)
	\textit{An arithmetic proof of Pop's Theorem concerning Galois groups of function fields over number fields}.
    J. reine angew. Math. \textbf{478}, 107\---126.
